Master's Project Journal

### 2019-04-21 thesis/Introduction.tex
79git statusgit statusgit statusgit statusgit statusgit statusgit statusgit statusgit statusgit statusgit statusgit status
start of conc

This thesis will put forward the \ac{FPGA} as a tool in the design of \ac{ADPLL} networks to bridge the gap between software simulations and implementation in custom silicon by providing a hardware-based simulation, modelling and validation platform. While an FPGA lacks the direct control over the schematic and layout that an \ac{ASIC} provides, the hardware nature of this platform enables the analysis of system dynamics that are not easily modelled in simulation and the testing.

@@

An \ac{FPGA} based test platform is ideal for those who wish to examine system dynamics without the time delays, financial burden or expertise required to develop a complete mixed-signal system on an \ac{ASIC} but retain the ability to realistically simulate the behaviour of an \ac{ADPLL} network. The result of this project is such a platform, designed to be extensible, with flexibility built into each component/module used.

>>>>

This thesis will put forward the \ac{FPGA} as a tool in the design of \ac{ADPLL} networks to bridge the gap between software simulations and implementation in custom silicon by providing a hardware-based simulation, modelling and validation platform. While an FPGA lacks the direct control over the schematic and layout that \iac{ASIC} provides, the hardware nature of this platform enables the analysis of system dynamics that are not easily modelled in simulation and the testing. \acp{ADPLL} are an entirely digital implementation of \iac{PLL}, advantageous as this allows for easier integration into the modern high transistor count \acl{IC} (\acs{IC}s) for which \ac{ADPLL} networks are a proposed clock distribution system.

@@

\Iac{FPGA} based test platform is ideal for those who wish to examine system dynamics without the time delays, financial burden or expertise required to develop a complete mixed-signal system on \iac{ASIC} but retain the ability to realistically simulate the behaviour of \iac{ADPLL} network. The result of this project is such a platform, designed to be extensible, with flexibility built into each component/module used.
